\section{Future works}

In this work, we have explored the foundations, methodologies, and applications of BNNs and their associated uncertainty estimation. However, this has to be interpreted as starting point in understanding the robustness of BNNs. We have demonstrated that leveraging uncertainty can indeed enhance robustness.

A crucial aspect for further investigation lies in assessing how network performance can be enhanced through the adoption of various methods and techniques aimed at improving robustness, such as data augmentation.

Another interesting aspect worthy of examination is the assessment of unknown values and their correlation with incorrect predictions. This analysis could provide valuable insights into the network efficiency in making accurate predictions.

Furthermore, we introduced the concept of confidence level in the context of classification with uncertainty. However, in this work, this concept was based on a linear approximation. It would be of interest to develop a more refined approximation method to enhance the interpretability of this parameter. Such refinement will improve the overall interpretability of estimated uncertainty which hold significant relevance in machine learning applications.

In conclusion, while our current research provides valuable insights into the capabilities of BNNs and their robustness through uncertainty, there are promising directions for future investigations to further advance our understanding and application of these techniques.